%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Xiaodong Yu, using the template from Kamil K Wojcicki
\documentclass[margin,line]{resume}

\setlength{\textwidth}{5.3in}
\setlength{\textheight}{10in}
\setlength{\topmargin}{-.250in}
\setlength{\hoffset}{1.4in}
%\setlength{\marginparwidth}{0.4in}
%\setlength{\parindent}{.4in}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Xiaodong Yu}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
	\section{\mysidestyle Contact\\Information}
	\begin{tabular}{p{3.5cm}p{10cm}}
	\textbf{E-mail}       &  dawnrain.yu@gmail.com  \\ 
	\textbf{Mobile}       & (202) 677-5816  \\ 
	\textbf{Location}       & Virginia Beach, VA  \\ 
	\end{tabular}


    \section{\mysidestyle LinkedIn}
    https://www.linkedin.com/in/yuxiaodong 
    \vspace{3mm}

     \section{\mysidestyle Work \\ Authorization}
    Permanent Resident of USA
    \vspace{3mm}
   
    %__________________________________________________________________________________________________________________
    % Skill Summary
    \section{\mysidestyle Qualification\\Summary}
         \begin{list2}
			\item  \textbf{Machine Learning Algorithm}: Linear Regression, Logistic Regression, Neural Networks and Deep Learning, Kernel Methods, Graphical Models, Random Forest, Mixture Models, Dimension Reduction, Approximate Inference, Sampling Methods, Continuous Latent Variables, Sequential Data, Combining Methods;
			\item  \textbf{Machine Learning Software Packages}: NumPy, SciPy, Scikit-Learn, TensorFlow, Pandas, Matplotlib;
			\item  \textbf{Programming}: C/C++, Python, Matlab, JavaScript, MySQL, MongoDB, Redis, Excel/VBA, AWS, Azure;
			\item  15+ years of research and development experience in machine learning;
                   \item   4+ years of experience as team leader in startup companies;
                   \item  Publications in the top-rated conferences and journals in machine learning and computer vision such as ICCV, ECCV, etc.;
                   \item  11 US and Chinese patents.
         \end{list2}
    
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}
    \textbf{University of Maryland}, College Park, MD       \\
    \vspace{-3mm}
    \begin{list2}
        \item \textbf{Ph.D.}, Electrical and Computer Engineering \hfill \textbf{2013} 
        \item \textbf{M.Sc.}, Electrical and Computer Engineering \hfill \textbf{2011}
    \end{list2}

    \textbf{National University of Singapore}, Singapore  \\
    \vspace{-3mm}
        \begin{list2}
        \item \textbf{M.Sc.}, Computer Science \hfill \textbf{2002}
    \end{list2}

    \textbf{University of Science and Technology of China}, Anhui, China  \\
    \vspace{-3mm}
        \begin{list2}
        \item \textbf{B.Eng.},  Electrical Engineering and Information Science \hfill \textbf{1999}
        \item \textbf{B.A.},  Business Administration \hfill \textbf{1999}
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Graduate Courses
    %\section{\mysidestyle Selected \\ Graduate \\Courses}
    %   \begin{list2}
	%		\item  ENEE620 Random Process (textbook ``Probability, Random Variables and Stochastic Processes'' ).
	%		\item  ENEE630 Advanced DSP (textbook ``Statistical Digital Signal Processing and Modeling'').
	%		\item  ENEE627 Information Theory (textbook ``Elements of Information Theory'').
	%		\item  ENEE633 Statistical and Neural Pattern Recognition (textbook ``Pattern Recognition and Machine Learning'').
	%		\item  CMSC726 Machine Learning (textbook ``The Elements of Statistical Learning'').
	%		\item  AMSC607 Advanced Numerical Optimization (textbook ``Stochastic Gradient Descent for Non-Smooth Optimization'', ``Distributed Optimization and Statistical Learning'', etc).
	%		\item  GPA: 3.83/4.00.
       %  \end{list2}
    
     %__________________________________________________________________________________________________________________
    
    % Teaching Experience
    \section{\mysidestyle Mentoring \& Teaching\\Experience}
         \begin{list2}
			\item  Mentoring junior data scientists and interns in company.
			\item  Tutorials on deep learning and computer vision on Norfolk Data Science meetup.
			\item  Talks on AI and its application towards investors, customers and business partners. 
			\item  Oral presentations at international machine learning conferences.

         \end{list2}
         
     %__________________________________________________________________________________________________________________
         % Industry Experience
    \section{\mysidestyle Industry\\Experience}
         \textsl{Founder and CTO} \hfill \textbf{2017-2019}\\
         \textbf{Jizhi Information Technology LLC}, Shanghai, China
         \begin{list2}
               \item Managing an R\&D team to provide consulting service on machine learning, data mining and visualization; 
               \item For customers in the financial industry, we developed a set of automatic fraud detection and risk management tools, which significantly reduced the cost and time spent on screening potential customers;
               \item For customers in the taxation service industry, we developed a set of automatic compliance risk detection tools, which eliminated most of the potential problems with only about 10\% of the cost with comparison to traditional methods.
         \end{list2}

         \textsl{Founder and CTO} \hfill \textbf{2015-2017}\\
         \textbf{Tiyun Technology LLC}, Beijing, China
         \begin{list2}
               \item Leading an R\&D team to develop customer analytics solutions for online retailers and manufacturers of shoes and clothing. Our patented machine learning algorithm can collect 3D data of the buyer's body and predict the correct dimension of his/her shoes and clothing. Our technology not only greatly reduced the cost of data collection (from 2 hours to 5 minutes), but also discovered new patterns in the Big Data of a particular population, which greatly facilitates new business models such as C2M (Customer To Manufacturers). 
         \end{list2}

         \textsl{Senior Researcher} \hfill \textbf{2011 - 2014}\\
         \textbf{Comcast Labs}, Washington, DC
         \begin{list2}
               \item Researching and prototyping on novel machine learning and Big Data algorithms to support Comcast's need for innovative solutions in the areas of customer analytics and operations analytics. Sample projects include user history analysis, VOD viewership prediction, content popularity prediction, user preference forecasting, recommendation system, etc.
         \end{list2}
             
         \textsl{Research and Development Engineer} \hfill \textbf{2007 - 2008}\\
         \textbf{ADF Solutions Inc.}, Silver Spring, MD
         \begin{list2}
             \item Developing a fast sub-image and near-duplicate image retrieval system;
             \item Developing an image classification system for digital forensics applications.
         \end{list2}
     
         \textsl{Software Engineer} \hfill \textbf{2001 - 2003}\\
         \textbf{Vislog Technology Pte. Ltd.}, Singapore
         \begin{list2}
             \item Developing a human segmentation and tracking system for visual surveillance;
             \item Developing a system of foreground segmentation and event detection within an Axis IP camera for real-time transmission of surveillance video over narrow band channels.
         \end{list2}
     
    %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Academia \\Experience}        
    \textsl{Graduate Research Assistant} \hfill \textbf{2009 - 2011}\\
    Computer Vision Lab, \textbf{University of Maryland}, College Park, MD
    \begin{list2}
    	\item Action attribute detection from sports videos with contextual constraints;
       \item Active scene understanding by combining vision and language;
       \item Transfer learning of object categories by employing ontological knowledge.
    \end{list2}

    \textsl{Graduate Research Assistant} \hfill \textbf{2004 - 2007}\\
    Language And Media Processing Laboratory, \textbf{University of Maryland}, College Park, MD
    \begin{list2}
        %\item Sub-image matching and near-duplicate image retrieval;
        \item Similar image clustering of images downloaded from the Internet;
        \item Shape descriptors for object recognition, language identification and image classification.
    \end{list2}

    \textsl{Associated Research Scientist} \hfill \textbf{2003 - 2004}\\
    School of Electrical and Electronic Engineering, \textbf{Nanyang Technological University}, Singapore
    \begin{list2}
        \item Content-based video semantic analysis and indexing.
    \end{list2}

    \textsl{Graduate Research Assistant} \hfill \textbf{1999 - 2001}\\
    Institute for Infocomm Research, \textbf{National University of Singapore}, Singapore
    \begin{list2}
        \item Video analysis and indexing based on MPEG motion vectors, with application to traffic surveillance, sports video classification and figure/ground segmentation.
    \end{list2}

    %__________________________________________________________________________________________________________________
    % Awards
   \section{\mysidestyle Awards}
	       \begin{list2}
		        \item  \textbf{Recognition Award}, Global AI Hackathon in Shanghai, 2017.
		        \item \textbf{First Place}, Google Tango Hackathon in Shenzhen, 2016.
		        \item \textbf{Inventor Recognition Award}, Comcast Labs, 2013.
		        \item  \textbf{STAR Award}, Comcast Labs, 2012.
		        \item  \textbf{Second Place}, Semantic Robot Vision Challenge joint with AAAI, 2007.	        
	        \end{list2}
       
        
        
       
    



%Last Updated: May 2019

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}


%______________________________________________________________________________________________________________________
% EOF

